\bf Calendar-based graphics for visualizing people's daily schedules

### 2018-10-22 cover-letter/cover-letter.Rmd

---
from: Earo Wang
fromqualifications: B.Comm.(Hons)
fromtitle: PhD candidate
fromWWW: earo.me
fromemail: earo.wang@monash.edu
fromphone: +61 4 4919 1031
fromsignature: signature.png
toname: Dr McCormick
toaddress: Journal of Computational and Graphical Statistics
opening: Dear Dr McCormick
closing: Sincerely
spacing: 1.5
output: MonashEBSTemplates::letter
---

@@

This paper provides new graphical methods for organizing and visualizing temporal data, collected at sub-daily resolutions, into a calendar layout. It is useful to provide insights into people's daily schedules relative to events such as work days, weekends, holidays, and special events, based on calendar layouts. The calendar format is created using linear algebra, to restructure data, that can then be piped into ggplot2's plotting routines. Many options and variants are supported to make it broadly applicable.

@@

Thank you for receiving our manuscript and considering it for review. We appreciate your time and look forward to your response.

>>>>

---
from: Earo Wang
fromqualifications: B.Comm.(Hons)
fromtitle: PhD candidate
fromWWW: earo.me
fromemail: earo.wang@monash.edu
fromphone: +61 4 4919 1031
fromsignature: signature.png
toname: Editor
toaddress: Journal of Computational and Graphical Statistics
opening: Dear Dr McCormick,
closing: Sincerely
spacing: 1.4
output: MonashEBSTemplates::letter
---

@@

This paper provides new graphical methods for organizing and visualizing temporal data, collected at sub-daily resolutions, into a calendar layout. It is useful to provide insights into people's daily schedules relative to events such as work days, weekends, holidays, and special events, based on calendar layouts. The calendar format is created using linear algebra, to restructure data, that can then be piped into ggplot2's plotting routines. Many options and variants are supported to make it broadly applicable. The methods are implemented in R package **sugrrants**, which is on CRAN. The paper is written in RMarkdown, which contains the R code to reproduce the results.

@@
